---
title: ""
author: ""
date: ""
output: word_document
---

 
```{r,results='hide',echo=FALSE,message=FALSE,warning=FALSE}
source('00_Data_setup.R')
source('01_Row_functions.R')
source('02_Table_functions.R')
source('03_Model_functions.R')

library(knitr)
####################################################################################################

####################################################################################################
                                      #Descriptive Tables #
####################################################################################################

###########################################################
#Table for two categories- fill in variable list for each type of variable#
###########################################################
#Use iris data with two categories
dat<-data[data$Species!='Virginica',]
dat$Species<-as.factor(as.character(dat$Species))
###############

a<-c('sepal_di') #categorical variables
b<-c('sepal_di') #categorical with only one row output
c<-c('Sepal.Length','Petal.Length') #continuous - regular mean
d<-c('Sepal.Width') #continuous - geometric mean
e<-'none' #continuous - geometric mean with +1-1
f<-'Petal.Width' #Wilcoxon rank-sum, median(IQR)
group<- dat$Species
tab_2_groups<-tab_2(a,b,c,d,e,f,group)


#############################################################################
#Table for three categories- fill in variable list for each type of variable#
#############################################################################
#use original dataset with three groups
dat<-data
############
a<-c('sepal_di') #categorical variables
b<-c('sepal_di') #categorical with only one row output
c<-c('Sepal.Length','Petal.Length') #continuous - regular mean
d<-c('Sepal.Width','Petal.Width') #continuous - geometric mean
e<-'none' #continuous - geometric mean with +1-1
group<-dat$Species # group variable
tab_3_groups<-tab_3(a,b,c,d,e,group)


####################################################################################################
                                      #Models#
####################################################################################################

tab_model_results<-fx_model_linear('Sepal.Length','Species')

```

#Statistical Methods
Demographic and clinical characteristics were compared using two-sample t-tests and Fisher's exact tests for continuous and categorical variables, respectively. Variables were visually assessed for skewness and log-transformed when appropriate. Significance was set at 0.05. R version 3.1.1 software (R Foundation for Statistical Computing, Vienna, Austria, http://www.R-project.org/) and rmarkdown: Dynamic Documents for R. R package version 0.3.3. http://CRAN.R-project.org/package=rmarkdown were utilized.

Results presented are based on the dataset `r data_set_name`.     

#Results

##Descriptive




**Table 1. Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab_2_groups)
```

*Geometric Mean and 95% CI

**Median and IQR


**Table 2.  Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab_3_groups)
```

*Geometric Mean and 95% CI

##Models


**Table 2. Regression results**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab_model_results)
```

