---
title: ""
author: ""
date: ""
output: word_document
---

 
```{r,results='hide',echo=FALSE,message=FALSE,warning=FALSE}
#packages to install
install.packages('knitr')
install.packages('devtools')
install.packages('roxygen2')

#install my package
library(devtools)
install_github('palmercl/Table1')

#load additional packages
library(knitr)
library(Hmisc)
library(Table1)

####################################################################################################

####################################################################################################
                                      #Descriptive Tables #
####################################################################################################
data_set_name<-'R Built-in Iris'

#create dichotomous variable
iris$sepal_di<-as.factor((iris$Sepal.Length<5)*1)

#set factor levels
levels(iris$sepal_di)=c("<5",'>=5')
levels(iris$Species)=c('Setosa','Versicolor','Virginica')

#Set Labels
label(iris$sepal_di)='Sepal Length'
label(iris$Sepal.Length)="Sepal Length"
label(iris$Sepal.Width)='Sepal weight'
label(iris$Petal.Length)='Petal Length'
label(iris$Petal.Width)='Petal Width'

###########################################################
#Table for n categories#
###########################################################

#Use iris data with two categories
test1<-iris[iris$Species!='Setosa',]
test1$Species<-as.factor(as.character(test1$Species))

#Use iris data with one category
test2<-iris[iris$Species=='Setosa',]
test2$Species<-as.factor(as.character(test2$Species))
################################################################################################
                                          ########
                                          #Tables#
                                          ########
#Three groups
tab1<-final_table(iris,c('Sepal.Length','Petal.Length','Sepal.Width','Petal.Width','sepal_di'),
                  iris$Species,1,T,2)
#Two groups
tab2<-final_table(test1,c('Sepal.Length','Petal.Length','Sepal.Width','Petal.Width','sepal_di'),
                  test1$Species,1,F)
#One group
tab3<-final_table(test2,c('Sepal.Length','Petal.Length','Sepal.Width','Petal.Width','sepal_di'),
                  test2$Species,2,T,1)
################################################################################################

```

#Statistical Methods
Demographic and clinical characteristics were compared using two-sample t-tests, Wilcox rank-sum tests, and chi-square tests for continuous, non-normally distributed continuous and categorical variables.  Significance was set at 0.05. R version 3.1.1 software (R Foundation for Statistical Computing, Vienna, Austria, http://www.R-project.org/) and rmarkdown: Dynamic Documents for R. R package version 0.3.3. http://CRAN.R-project.org/package=rmarkdown were utilized.

Results presented are based on the dataset `r data_set_name`.     

#Results

##Descriptive

**Table 1. Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab1)
```
*Median and IQR


**Table 2.  Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab2)
```

*Median and IQR

**Table 3.  Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab3)
```

*Median and IQR




