---
title: ""
author: ""
date: ""
output: word_document
---

 
```{r,results='hide',echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(moments)

source('00_Data_setup.R')
source('01_Row_functions.R')
source('02_Table_functions.R')
source('03_Model_functions.R')
####################################################################################################

####################################################################################################
                                      #Descriptive Tables #
####################################################################################################

###########################################################
#Table for n categories#
###########################################################
#Use iris data with two categories
dat<-data[data$Species!='Setosa',]
dat$Species<-as.factor(as.character(dat$Species))

################################################################################################
#vector with variables and group/ treatment variable
tab1<-final_table(c('sepal_di','Sepal.Length','Petal.Length','Sepal.Width','Petal.Width'),dat$Species)

################################################################################################
#use original dataset with three groups - function automatically adjusts to # of groups
dat<-data
############
#vector with variables and group/ treatment variable
tab2<-final_table(c('sepal_di','Sepal.Length','Petal.Length','Sepal.Width','Petal.Width'),dat$Species)

####################################################################################################
                                      #Models#
####################################################################################################

tab_model_results<-fx_model_linear('Sepal.Length','Species')

```

#Statistical Methods
Demographic and clinical characteristics were compared using two-sample t-tests, Wilcox rank-sum tests, and chi-square tests for continuous, non-normally distributed continuous and categorical variables.  Significance was set at 0.05. R version 3.1.1 software (R Foundation for Statistical Computing, Vienna, Austria, http://www.R-project.org/) and rmarkdown: Dynamic Documents for R. R package version 0.3.3. http://CRAN.R-project.org/package=rmarkdown were utilized.

Results presented are based on the dataset `r data_set_name`.     

#Results

##Descriptive

**Table 1. Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab1)
```
*Median and IQR


**Table 2.  Demographic and Clinical Characteristics**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab2)
```

*Median and IQR

##Models

**Table 3. Regression results**
```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE}
kable(tab_model_results)
```

